BOOK{lshort-cn,
        author =       {C\TeX{}~翻译小组},
        title =        {lshort~中文版~3.20},
        year =         {2003},
}

BOOK{deng:01a,
        author =       {{邓建松,~彭冉冉,~陈长松}},
        title =        {\LaTeXe{}~科技排版指南},
        publisher =    {科学出版社,~书号:~7-03-009239-2/TP.1516},
        year =         {2001},
        address =      {北京},
}

BOOK{wang:00a,
        author =       {王磊},
        title =        {\LaTeXe{}~插图指南},
        year =         {2000},
}

BOOK{zhang:03a,
        author =       {张林波},
        title =        {关于新版~CCT~的说明},
        year =         {2003},
}

book{lamport85a,
        author={Leslie Lamport},
        title={{LaTeX} --- A Document Preparation System: User's Guide and Reference Manual},
        publisher={Addison-Wesley},
        year={1985},
        address={Reading, Massachusetts},
        edition={2nd}
}

book{knuth86a,
        author={Donald E. Knuth},
        title={The {TeX}book},
        publisher={Addison-Wesley},
        year={1986},
        volume={A},
        address={Reading, Massachusetts},
        series={Computers and Typesetting}
}

book{knuth86b,
        author={Donald E. Knuth},
        title={{TeX}: The Program},
        publisher={Addison-Wesley},
        year={1986},
        volume={B},
        address={Reading, Massachusetts},
        series={Computers and Typesetting}
}

book{knuth86c,
        author={Donald E. Knuth},
        title={The {METAFONT}book},
        publisher={Addison-Wesley},
        year={1986},
        volume={C},
        address={Reading, Massachusetts},
        series={Computers and Typesetting}
}

book{knuth86d,
        author={Donald E. Knuth},
        title={{METAFONT}: The Program},
        publisher={Addison-Wesley},
        year={1986},
        volume={D},
        address={Reading, Massachusetts},
        series={Computers and Typesetting}
}

book{knuth86e,
        author={Donald E. Knuth},
        title={Computer Modern Typefaces},
        publisher={Addison-Wesley},
        year={1986},
        volume={E},
        address={Reading, Massachusetts},
        series={Computers and Typesetting}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CHAPTER 前言
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%吕才典讲义 
@book{2014lv,
      author = {{吕才典}},
      title = "粒子物理学",
      year = {2014},
      publisher = "讲义，中科院高能所",
}

% higgs
@article{ATLAS:2012,
      author         = "G. Aad. and others",
      title          = "{(ATLAS Collaboration)}",
      collaboration  = "ATLAS",
      journal        = "Phys.Lett.B",
      volume         = "716",
      year           = "2012",
      pages          = "1-29"
}

% higgs
@article{CMS:2012,
      author         = "S.Chatrchyan. and others",
      title          = "{(CMS Collaboration)}",
      collaboration  = "CMS",
      journal        = "Phys.Lett.B",
      volume         = "716",
      year           = "2012",
      pages          = "30-61"
}

@book{duds2015,
      author = {{杜东生,~杨茂志}},
      title = "粒子物理导论",
      year = {2014},
      publisher = "北京科学出版社",
}

@book{zhangns2015,
      author = {{章乃森}},
      title = "粒子物理学[M]",
      year = {1968},
      publisher = "北京科学出版社",
      address =      {北京}，
      pages          = "1-78",
}

% SM
@article{S.Weinberg:1967,
      author         = "S. Weinberg..",
      title          = "{A Model of Leptons[J]}",
      journal        = "Phys. Rev. Lett.",
      volume         = "19",
      year           = "1967",
}

@book{tangxw1982,
      author = {{唐孝威主编}},
      title = "粒子物理实验方法",
      year = {1982},
      publisher = "高等教育出版社",
}

@book{xukz1981,
      author = {{徐克尊等编}},
      title = "粒子探测技术",
      year = {1981},
      publisher = "上海科学技术出版社",
}

@book{xieyg2003,
      author = {{谢一冈等主编}},
      title = "粒子探测器与数据获取",
      year = {2003},
      publisher = "科学出版社",
}
@book{xuefj2003,
      author = {{薛凤家等主编}},
      title = "诺贝尔物理学奖百年回顾",
      year = {2003},
      publisher = "国防工业出版社",
}

@book{zhengzp2009,
      author = {{郑志鹏主编}},
      title = "北京谱仪II正负电子物理(第一版)",
      year = {2009},
      publisher = "中国科学技术大学出版社",
}

@book{wangyf2011,
      author = {{王贻芳主编}},
      title = "北京谱仪(BESIII)的设计与研制",
      year = {2011},
      publisher = "上海科学技术出版社",
}

% @book{wangyf2011ww,
      author = {{王贻芳主编}},
      title = "北京谱仪(BESIII)的设计与研制",
      year = {2011},
      publisher = "上海科学技术出版社",
      pages     = "464-510"
}

@article{BESIII:2013,
      author         = "M.Ablilim. and others",
      title          = "{(BESIII Collaboration)}",
      collaboration  = "BESIII",
      journal        = "Phys.Rev.Lett",
      volume         = "110",
      year           = "2013",
      pages          = "252001"
}

@article{yuancz:2002,
      author         = "Yuan C Z. and others",
      journal        = "高能物理与核物理",
      volume         = "24(12)",
      year           = "2002",
      pages          = "1201"
}

@article{chaokt:2009,
      author         = "Chao K T, Wang Y F. and others",
      title          = "{physics at BESIII}",
      journal        = "Int. J. Mod. Phys.",
      volume         = "A 24(1)",
      year           = "2009"
}

@book{xiejl1996,
      author = {{谢家麟等}},
      title = "北京正负电子对撞机和北京谱仪",
      year = {1996},
      publisher = "浙江科学技术出版社,ISBN7-5341-0721-0",
}

@article{ihep:2003,
      author = {{中国科学院高能物理研究所}},
      title = "{BEPCII初步设计报告}",
      year = {2003}
}

@article{ihep:2006,
      author = {{中国科学院高能物理研究所}},
      title = "{北京正负电子对撞机重大改造工程(BEPCII)}",
      year = {2006}
}

@article{M.A:2010,
      author         = "M.Ablikim. and others",
      title          = "{Design and Construction of the BESIII Detector}",
      journal        = "Nuclear Instruments and Methods in Physics Research A",
      volume         = "614",
      year           = "2010",
      pages          = "345-399"
}

@article{ruanlj:2005,
      author         = "阮丽娟等",
      title          = "{TOFr在STAR实验中的标定}",
      journal        = "高能物理与核物理",
      volume         = "29",
      year           = "2005",
}
@article{wuj:2005,
      author         = "jian wu. and others",
      title          = "{The performance of the TOFr tray in STAR}",
      journal        = "Nuclear Instruments and Methods in Physics Research A",
      volume         = "538",
      year           = "2005",
      pages          = "243-248"
}

@article{wangy:2010,
      author         = "Yi Wang. and others",
      title          = "{Production and quality control of STAR-TOF MRPC}",
      journal        = "Nuclear Instruments and Methods in Physics Research A",
      volume         = "613",
      year           = "2010",
      pages          = "200-206"
}

@article{M:2014,
      author         = " M. Ullrich. and others",
      title          = "{Implementation of a Multigap-Resistive Plate-Chamber as Time of Flight Detector into the BOSS Framework}",
      year           = "April 6,2014",
      edition={Version 1.10}
}
@article{A.A:2005,
      author         = "A. Akindinov. and others",
      title          = "{Performance of the ALICE Time-Of-Flight detector at the LHC}",
      journal        = "Eur. Phys. J. Plus",
      volume         = "128",
      year           = "2013"
}

@article{A.Alici:2012,
      author         = "A. Alici",
      title          = "{Status and performance of the ALICE MRPC-based Time-Of-Flight detector}",
      journal        = "Jinst",
      volume         = "7",
      year           = "2012",
}

@article{A.Alici:2014,
      author         = " A. Alici",
      title          = "{Particle identification with the ALICE Time-Of-Flight detector at the LHC}",
      journal        = "Nuclear Instruments and Methods in Physics Research A",
      volume         = "766",
      year           = "2014",
      pages          = "288-291"
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CHAPTER 第一章
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@article{zhaoc:2011,
      author         = "ZHAO Chuan. and others",
      title          = "{Time calibration for the end cap TOF system of BESIII}",
      journal        = "Chinese Physics C",
      volume         = "35(1)",
      year           = "Jan., 2011",
      pages          = "72-78"
}

@book{wangxz2016,
      author = {{王小状}},
      title = "{北京谱仪端盖飞行时间探测器升级改造的MRPC性能研究}",
      year = {2016},
      publisher = "中国科学技术大学博士论文"
}

@article{he:2014,
      author         = "K.L.He",
      title          = "{Status and Plan for Analysis and Tools software}",
      journal        = "BESIII CollaborationMeeting",
      year           = "2007"
}


@article{liwd:2006,
      author         = "Li W D,Liu H M. and others",
      title          = "{Proceeding of CHEP06}",
      year           = "February 13-17,2006",
      address        = "{Mumbai}"
}
 
@article{Barrand:2000,
      author         = "Barrand G. and others",
      title          = "{Proceeding of CHEP2000}",
      year           = "February 6-12,2000",
      address        = "{Padova}"
}

@misc{root,
      title          = {root},
      howpublished   = {\url{http://root.cern.ch/}}
}

@misc{cern,
      title          = {cern},
      howpublished   = {\url{http://cernlib.web.cern.ch/cernlib/.}}
}

@article{max:2007,
      author         = "马想等",
      title          = "{}",
      journal        = "核电子学与探测技术",
      year           = "2007",
      volume         = "27(4)",
      pages          = "670"
}

@article{zhangxm:2005,
      author         = "张晓梅等",
      title          = "{}",
      journal        = "核电子学与探测技术",
      year           = "2005",
      volume         = "25(6)",
      pages          = "638"
}

@book{wulh2007,
      author = {{伍灵慧}},
      title = "{BESIII漂移室离线刻度研究及模型的束流测试}",
      year = {2007},
      publisher = "中国科学院高能物理研究所博士论文"
}

@book{wangjk2009,
      author = {{王纪科}},
      title = "{BESIII径迹拟合算法与GPUPWA的相关开发}",
      year = {2009},
      publisher = "中国科学院高能物理研究所博士论文"
}

@article{wangll:2014,
      author         = "王亮亮等",
      title          = "{BESⅢ主漂移室径迹的外推和径迹匹配}",
      journal        = "高能物理与核物理",
	  volume         = "31(2)",
      year           = "Feb.,2007"
}

@article{Maxiang:2008,
      author         = "Ma Xiang. and others",
      title          = "{Determination of event start time at BESIII}",
      collaboration  = "BESIII",
      journal        = "Chinese Physics C.",
      volume         = "32(9)",
      year           = "Sep., 2008"
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CHAPTER 第二章
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STAR
@article{Shao:2009aa,
      author         = "Ming Shao. and others",
      title          = "{Upgrade of the calibration procedure for a STAR time-of-flight detector with new electronics}",
      collaboration  = "Star",
      journal        = "IOP science.",
      volume         = "20",
      year           = "2009",
      pages          = "025102",
      doi            = "10.1088/0957-0233/20/2/025102",
      url            = "stacks.iop.org/MST/20/025102
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CHAPTER 第三章
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bian
@article{Bian:2010aa,
      author         = "BIAN jian-Ming. and others",
      title          = "{Abosolute photon energy calibration for the BESIII EMC}",
      collaboration  = "CPC",
      journal        = "Chinese Physics C",
      volume         = "34",
      year           = "2010",
      pages          = "72-77"
}

% Nov
@article{Nov:2000aa,
      author         = "Bauer A J M.",
      title          = "{BaBar Note 521}",
      year           = "2000",
%      pages          = "521"
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CHAPTER 第六章
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@book{2007hjf,
      author = {{胡继峰}},
      title = "{BESⅢ飞行时间计数器的刻度方法及离线软件}",
      year = {2007},
      publisher = "中国科学技术大学硕士论文"
}

@book{zhuys2006ss,
      author = {{朱永生}},
      title = "实验物理中的概率和统计",
      year = {2006},
      publisher = "科学出版社",
      pages     = "291-352"
}

@book{C++Primer,
      author = {{Stanley B.and other著，王刚，杨巨峰译}},
      title = "C++中文版（第五版）",
      year = {2013},
      publisher = "电子工业出版社",
%      pages     = "291-352"
}